Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-11-13 Paper/ms.tex
Fengji's Z

The marginal likelihood was $\ln(\mathcal{Z}) \approx -618.04$ and the
information was $\mathcal{H} \approx 140.2$ nats. This compares favourably
to the marginal likelihood of $-640.1$ found by \citet{fengji}, although it
is unclear whether we used exactly the same dataset.

>>>>

The marginal likelihood was $\ln(\mathcal{Z}) \approx -618.04$ and the
information was $\mathcal{H} \approx 140.2$ nats. This compares favourably
to the marginal likelihood of $-640.1$ (for a 6-planet model)
found by \citet{fengji}, although it is unclear whether we used exactly the
same dataset.
